\section*{Procedure}

The air track and compressor were set up by the lab instructors prior to our experiment. We ensured that the track was level by adjusting the base support screws until a glider placed in the middle of the track remained stationary. We then placed a photo gate 30 cm from each end of the track and attached a rubber band bumper to each end of the track.

\bigskip

To avoid excessive verbosity, we note now that the mass of each glider was measured after adding or removing any accessories or weights, giving us $m_1$ and $m_2$ to later calculate $p$ and $KE$.

\bigskip

To observe inelastic collisions, we attached a nail to glider 1 and a wax tube to glider 2. While recording input from the photo gates using the computer, we pushed glider 1 from one end of the track toward glider 2, which remained stationary between the two photo gates. This allowed us to take $v_i$ since $v_i = v_{i, 1} + v_{i, 2}$ and $v_{i, 2} = 0$. After the collision, we recorded $v_f$ as the two gliders -- stuck together following the inelastic collision -- passed through the photo gate on the opposite end of the track from where glider 1 was pushed. This trial was repeated three times for which $m_1 = m_2$, and three more times for which $m_1 > m_2$.

\bigskip

To observe elastic collisions, we removed the accessories from the gliders and replaced each with a rubber band bumper so that the gliders would initiate contact with their bumpers. We noted that in an elastic collision, $v_{f, 1}$ and $v_{f, 2}$ would be recorded separately since the gliders would not become attached to one another after the collision. Similarly to the inelastic collisions, we repeated the trial three times with $m_1 = m_2$, and three times with $m_1 > m_2$.

\bigskip

After recording all of the data from the four trials, we used the initial values of $m$ and $v$ to calculate $p$ and $KE$ for each trial. We used the final values of $m$ and $v$ to calculate $p'$ and $KE'$ for each trial. With these calculations, we found the percent difference between $p$ and $p'$ (and between $KE$ and $KE'$) for each trial, and we calculated the average percent difference for each trial.
